---
title: "Reference Image Export"
output: html_notebook
---


```{r}

require(readr)
require(fs)
require(dplyr)

```

## Full Export - Subset for Reference = True + By Region
```{r}

Nref = read.csv('https://github.com/rytomey/msRRV/raw/main/refIMAGES/refRSA.csv')
Cref = read.csv('https://github.com/rytomey/msRRV/raw/main/refIMAGES/refAWMA.csv')
Sref = read.csv('https://github.com/rytomey/msRRV/raw/main/refIMAGES/refBC.csv')

```

# REDSTONE 

### Columns used to Pull Images
```{r}

photo_paths =  Nref$Absolute.Path
to_download =  Nref$Reference
species     =  Nref$Species
behavior    =  Nref$Behavior

```


### Folder + Loop Behavior Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Nbehavior"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    behavior_folder_name = paste0(behavior[i], "_photos")
    behavior_folder = file.path(local_folder, behavior_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(behavior_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(behavior_folder, file_name), overwrite = TRUE)
  }
}


```

### Folder + Loop Species Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Nspecies"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    species_folder_name = paste0(species[i], "_photos")
    species_folder = file.path(local_folder, species_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(species_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(species_folder, file_name), overwrite = TRUE)
  }
}


```


# AUTAUGA

### Columns used to Pull Images
```{r}

photo_paths =  Cref$Absolute.Path
to_download =  Cref$Reference
species     =  Cref$Species
behavior    =  Cref$Behavior

```


### Folder + Loop Behavior Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Cbehavior"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    behavior_folder_name = paste0(behavior[i], "_photos")
    behavior_folder = file.path(local_folder, behavior_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(behavior_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(behavior_folder, file_name), overwrite = TRUE)
  }
}


```

### Folder + Loop Species Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Cspecies"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    species_folder_name = paste0(species[i], "_photos")
    species_folder = file.path(local_folder, species_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(species_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(species_folder, file_name), overwrite = TRUE)
  }
}


```





# BALDWIN

### Columns used to Pull Images
```{r}

photo_paths =  Sref$Absolute.Path
to_download =  Sref$Reference
species     =  Sref$Species
behavior    =  Sref$Behavior

```


### Folder + Loop Behavior Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Sbehavior"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    behavior_folder_name = paste0(behavior[i], "_photos")
    behavior_folder = file.path(local_folder, behavior_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(behavior_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(behavior_folder, file_name), overwrite = TRUE)
  }
}


```

### Folder + Loop Species Picture Pull
```{r}

local_folder = "C:/Users/rylee/OneDrive - Auburn University/FAVimages/Sspecies"

for (i in 1:length(photo_paths)) {
  if (to_download[i]) {
    file_name = basename(photo_paths[i])
    species_folder_name = paste0(species[i], "_photos")
    species_folder = file.path(local_folder, species_folder_name)
    
    # Create species folder if it doesn't exist
    dir_create(species_folder, recurse = TRUE)
    
    # Copy the photo to the species folder
    file_copy(photo_paths[i], file.path(species_folder, file_name), overwrite = TRUE)
  }
}


```

